A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 6_validation.tex
Zjenja: discussion edits

From the experimental results shown in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $10^{-5} n \log n$ seconds.
The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.

@@

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{1}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation per strategy.
\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of our strategies 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'. 
These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.
We compared the width uniformity of the 6 outer beads for the strategies 'Inward distributed' and 'Evenly distributed'.

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive segments generated by each strategy.
The relative frequency of these angles is shown in \cref{smoothness}.
All strategies show a higher number of corners for smaller angles with a peak towards 0 degrees (straight line).
The Inward  'Evenly distributed' strategy produces an order of magnitude more corners around 30 degrees.
While 
 we found no significant differences in the smoothness of the toolpaths generated by the other strategies.

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the depositioning control system some of the prints show defects.
Such defects are less prevalant for the inward distributed beading strategy than the other strategies.

>>>>

From the experimental results shown in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $2*10^{-5} n \log n$ seconds.
The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.

@@

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{1}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation per strategy.
\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of our strategies 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'. 
These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.
We compared the width uniformity of the 6 outer beads for the strategies 'Inward distributed' and 'Evenly distributed', the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the 'Inward distributed' strategy clearly have more often the nominal width of \SI{400}{\micro\meter}, while the 'Evenly distributed' more often extrudes widths that deviate from the nominal width.

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive segments generated by each strategy.
The relative frequency of these angles is shown in \cref{smoothness}.
All strategies show a higher number of corners for smaller angles with a peak towards 0 degrees (straight line).
The 'Inward distributed' strategy produces an order of magnitude less corners around 30 degrees, compared to 'Evenly distributed'. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around 90 degrees.

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
We set the preferred width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the depositioning control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading strategy than the other strategies.

### 2019-08-23 8_discussion.tex
Zjenja: discussion edits

\subsection{Comparison of beading strategies}
The naive strategy and the single bead strategy are of little use to FDM printers, but they show the flexibility of our parametric system.

@@

The constant bead count beading strategy effectively deals with all overfills and underfills, but at the cost of wildly differing bead widths.
See \cref{TEST_Constant_accuracy}.
Note that around regions where the bead width changes a lot we can see some overfill areas, which explains the unusually high overfill statistic in \cref{over_underfill}.
Because the bead count 
For an input outline shape which contains both very small and very large features the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.

If we look at \cref{TEST_Center_accuracy} we can see that
the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width, which is still quite a bit.
According to \cref{over_underfill} the overfill and underfill of the over- and underfill for the centered, the evenly distributed and the inward distributed strategy are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the naive method.

However, according to \cref{widthHistogram} the centered strategy exhibits a lot wider range of bead widths than the distributed strategies:
the standard deviation of the bead widths in the centered beading strategy is approximately \SI{38}{\micro\meter}, while the standard deviation resulting from the distributed strategies is approximately \SI{15}{\micro\meter}.
We can therefore state that the distributed strategies result in bead widths closer to the nominal bead widths than the centered strategy, which means that the distributed strategies realize the mechanical properties associated to a given nominal bead width more closely.

The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
Also when looking at \cref{smoothness} we cannot conclude any difference in the smoothness between the evenly distributed and the inward distributed beadign strategy.
We do not provide any statistical evidence that the inward distributed beading strategy is in fact better than the evenly distributed strategy.

However, we can say that by looking at \cref{distributed_comparison} we see that the outer toolpaths have the nominal bead width more often, which means that the inaccuracies of the adaptive bead width deposition system affect the dimensional accuracy of the outline shape less.
The errors from such inaccuracies and the errors in mechanical properties due to deviation from the nominal bead width are located near the center of the shape, which means the overal mechanical properties of the part are least affected by the discrepancy between the actual feature size and the preferred feature size when using the inward distributed beading strategy.

>>>>

\subsection{Comparison of beading strategies}
The 'Naive' strategy and the 'Outer bead' strategy are of little use to FDM printers, but they show the flexibility of our parametric system.

@@

The 'Constant bead count' strategy effectively deals with underfills, but generates orders of magnitude more overfills compared to the other strategies. 
Also, the strategy comes at the cost of greatly varying bead widths and an average bead width that is not close to the nominal bead width.
Note that most overfill areas occur near regions of alternating bead width.

For an input outline shape which contains both very small and very large features, the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.

If we look at \cref{TEST_Center_accuracy} we can see that
the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
According to \cref{over_underfill} the overfill and underfill for the 'Centered', the 'Evenly distributed' and the 'Inward distributed' strategy are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the naive method.

However, according to \cref{widthHistogram} the Centered strategy exhibits a lot wider range of bead widths than the Distributed strategies:
the standard deviation of the bead widths in the Centered strategy is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the Distributed strategies is approximately \SI{14}{\micro\meter}.
We can therefore state that the Distributed strategies result in bead widths closer to the nominal widths compared to the Centered strategy.
This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

The Inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.

However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all. 
Also, we find that compared to Evenly distributed, the Inward distributed strategy produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}). 
Therefore, when using the Inward distributed strategy the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a a low percentage.
